% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\definecolor{newgrey}{gray}{0.50}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
Phone: 1 (236)-777-3579 & \textbf{\huge Jiasen \textcolor{newgrey}{XU}}\\
Email: jiasenxu@gmail.com\\
LinkedIn: \url{www.linkedin.com/in/jiasenxu} & 1201-488 Marine Dr SW\\
Github: \url{https://github.com/JasonMrX} & Vancouver, BC, V5X0C6\\
\end{tabular*}

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\itemsep0em
\item
	\ressubheading{University of Waterloo}{Waterloo, Canada}{M.Eng in Electrical \& Computer Engineering (GPA: 94.8/100)}{Sept. 2014 - Sept. 2016}
	\begin{itemize}
        \resitem{Graduate Research Scholarship and Faculty of Engineering Award recipient}
	\end{itemize}
\item
	\ressubheading{University of Science and Technology of China}{Hefei, China}{B.Eng in Electrical Engineering (GPA: 91.0/100)}{Sept. 2010 - Jul. 2014}
	\begin{itemize}
        \resitem{ \textbf{National Scholarship} recipient; ranked \textbf{10/311} in the School of Information Technology}
	\end{itemize}

\end{itemize}

\resheading{Experience}
\begin{itemize}
\itemsep0em
\item
    \ressubheading{Cloud Developer}{Vancouver, Canada}{SAP Canada Inc.}{ Nov. 2016 - Present}
	\begin{itemize}
        \resitem{Building SAP's next generation cloud-based Analytics platform -- SAP BusinessObjects Cloud.}
        \resitem{Ramped up within two weeks with no previous knowledge of Javascript or SAPUI5, and start feature ownership from elaborating design, implementation and unit/integration testing.}
        \resitem{Optimized performance by introducing lazy loading design pattern -- saved 20\% of page loading time on average.}
        \resitem{Greatly reduced code duplication by refactoring legacy code to be aligned with OO pattern.}
	\end{itemize}
\item
    \ressubheading{Software Developer}{Kitchener, Canada}{ApplyBoard Inc., a Startup Incubated in Velocity Garage}{ Jul. 2015 - Apr. 2016}
	\begin{itemize}
        \resitem{Join the dev team as the first developer besides CTO; actively contributed to \href{https://www.applyboard.com/student}{ApplyBoard.com} the main app as a full-stack Rails developer, which has 50k+ active user globally with 400k+ visits to date.}
		\resitem{In charge of testing automation, Search Engine Optimization (SEO), database schema design and migration.}
	\end{itemize}
\item
	\ressubheading{Research Assistant}{Waterloo, Canada}{University of Waterloo, Supervised by Professor En-Hui Yang}{Sep. 2014 - Apr. 2016}
	\begin{itemize}
		\resitem{Redesigned the quantizer in HEVC/H.265 to further improve video compression performance. Methodology is based on video content understanding using machine learning and statistical analysis tools.}
	\end{itemize}
\end{itemize}

\resheading{Notable Projects}
\begin{itemize}
\itemsep0em
\item
	\ressubheading{Enhance the Constanct Value Checker in \href{https://github.com/typetools/checker-framework}{the Checker Framework}}{}{Mentored by Professor Michael Ernst (MIT) and Professor Werner Dietl (Google)}{Jun. 2016 - Present}
	\begin{itemize}
        \resitem{The Checker Framework provides pluggable type checking for Java, which is built upon the Type Annotations compiler in Java 8 (JSR308). This project enhances the Constant Value Checker, one of the core checkers in the Checker Framework, which uses annotations to indicate the possible values of an expression at compile time.}
        \resitem{By introducing the @IntRange annotation and a complex set of range maths, the flexitbility and the precision of the constant value checker are greatly improved, making it easier to catch potential runtime exceptions, e.g. \textit{ArithmeticException} and \textit{ArrayIndexOutOfBoundsException}, at compile time.}
	\end{itemize}
\item
	\ressubheading{JPEG Image Decoder}{}{Individual side project}{Jan. 2015 - Jun. 2015}
	\begin{itemize}
		\resitem{Implemented a console application that are able to decode nearly all JPEG images within a second.}
        \resitem{Application can handle the prevalent Baseline/Progressive encoded images; multi-resolution decoding for Progressive encoded images is also supported.}
	\end{itemize}
	
\end{itemize}

\resheading{Highlight of Skills}
\begin{itemize}
\itemsep0em
\item {\textbf {Programming:}} Solid knowledge of algorithms and data structures; proficient in C/C{}\verb!++!, Java, JavaScript, Ruby and Matlab; contributed to various large open source projects; started programming since 11 years old (using Pascal!).
\item{\textbf {Web Development:}} Proficient in web development with Ruby on Rails, HTML, CSS and Javascript; Also experience with large-scale rich front-end JavaScript application with SAPUI5 and node.js.
\item{\textbf {Database System:}} Proficient in SQL; Hands-on experience in both NoSQL and relational databases
%\item{\textbf {Development Tools:}} 5 years' experience in Visual Studio and MATLAB; Proficient in Unix like OS, vim editor, Git/Github and Netbeans; Also experienced in Eclipse and Altera QuartusII
\item{\textbf {Development Tools:}} Familiar with VS/Matlab/Eclipse, Linux, vim, git/github/gerrit, ant/maven, travis/jenkins.
\item{\textbf {Research:}} 3 years' research experience in data compression, image processing and information theory; Expert in JPEG compression standard; In-depth understanding of HEVC/H.265 video compression standard
%\item{\textbf {Teamwork:}} Self-motivated, hard working and dedicated to high quality, with proven team work skills and leadership

\end{itemize}


\end{document}
